---
output: 
  word_document:
    reference_docx: Annual_Report_Format.docx
params:
  prj_cd: LEA_IA25_SHA
---

```{r Load Packages, include=FALSE}
#This section of code will load all required packages.

#General Data Manipulation
library(dplyr)
library(tidyr)
library(stringr)

#Download data from GLIS
library(glfishr)

#Figures & Tables
library(ggplot2)
library(flextable)
library(officer)
```

<!-- Title Page -->
<!-- Note: To have a line break without using ENTER, leave two trailing spaces. -->
<!-- The 'custom-style' sections refer to MS Word font styles in the 'Annual_Report_Format" document. -->

<!-- This section pulls data from GLIS. It also adds in species common names using the GLIS Common Application. -->

```{r Load GLIS Project Data, include=FALSE}
#Loads the required tables
FN011 <- get_FN011(list(prj_cd = params$prj_cd))
FN121 <- get_FN121(list(prj_cd = params$prj_cd))
FN123 <- get_FN123(list(prj_cd = params$prj_cd))

#Load the Species Common Table and update the species names to proper case
species <- get_species()
species <- species %>%
  select(SPC, SPC_NMCO, SPC_NMSC)%>%
  mutate(SPC_NMCO = str_to_title(SPC_NMCO))

#Append the SPC_NMCO field to FN123
FN123 <- merge(FN123, species, all.x = TRUE)
```

::: {custom-style="Title2"}
SARA Permit - Project Summary
:::

**Project Title:** Inner Bay Fish Community Hoop Net Survey  
**Permit Number:** 24-PCAA-00001  
**Authors:** Arthur Bonsall, Lake Erie Management Unit, MNR  
**Date Prepared:** `r Sys.Date()`

::: {custom-style="Heading 1"}
Introduction: 
:::

The inner bay of Long Point is located on the north shore of the eastern basin of Lake Erie. It is protected by the Long Point peninsula and sand shoals extending from Turkey Point and Pottohawk Point. These sheltered waters receive nutrient and other chemical inputs from Big Creek as well as from east to west oriented seiches which transport water from the main lake into the inner bay. With a mean depth of approximately 2m and dense macrophyte coverage, the inner bay supports important spawning and nursery habitat for several native fish species. As well, the inner bay also provides year-round refuge and foraging habitat for a number of warmwater fish species including species at risk such as Warmouth, Spotted Gar, and Lake Chubsucker. The inner bay also supports both a recreational sport fishery as well as a commercial fishery which harvests approximately $125,000 worth of fish annually.

The objective of the Inner Bay Fish Community Hoop Net Survey is to use a fishery-independent methodology to assess the springtime fish communities present in the inner bay of Long Point, Lake Erie. Fish community information will be used to inform management decisions related to both recreational and commercial fisheries.

::: {custom-style="Heading 1"}
Methods:
:::

Potential sampling sites were generated by creating 500m long shoreline segments extending from Pottohawk Point around the inner bay to Turkey Point. In total, 34 sample sites were randomly selected from the pool of potential sites. Sampling occurred from `r format(as.Date(FN011$PRJ_DATE0), "%B %d")` to `r format(as.Date(FN011$PRJ_DATE1), "%B %d")`, `r FN011$YEAR`. The fyke nets were 3’ high and 4’ wide composed of 1” square knotted nylon netting spread over seven 36” tapered steel hoops and were set perpendicular to shore in approximately 3’ of water. The nets had three funnel sections each with 12” openings. The leads were 150’ in length and 3’ high and the wings (2) were 10’ long and 3’ high. Buoys were placed in the nets to ensure that any air breathing animals caught incidentally in the net would be able to access the surface. Nets were set overnight for approximately 18-28 hours. Captured fish were removed from the net immediately and placed into a water bin. Fish were then identified, enumerated, measured, and released. Any non-fish species caught during the survey were identified, enumerated, and released.

<!-- This section pulls data from GLIS. It also adds in species common names using the GLIS Common Application. -->

```{r Get SPC Values, include=FALSE}
#Get the overall catch number
SPC_TOTAL <- sum(FN123$CATCNT)

#Get the total number of species
SPC_NUM <- nrow(FN123)

#Adjust catch counts for small mesh and summarize catch
SPC_SUM <- FN123 %>%
  group_by(SPC, SPC_NMCO, SPC_NMSC) %>% 
  summarize(CATCNT = sum(CATCNT)) %>%
  mutate(PER_CATCH = round((CATCNT/SPC_TOTAL)*100,0))%>%
  arrange(desc(CATCNT))%>%
  ungroup()
```


::: {custom-style="Heading 1"}
Results:
:::

A total of `r SPC_TOTAL` fish comprised of `r SPC_NUM` species were caught during the `r FN011$YEAR` Inner Bay Fish Community Hoop Net Survey. `r SPC_SUM$SPC_NMCO[1]` (n=`r SPC_SUM$CATCNT[1]`) was the most abundant species, representing `r SPC_SUM$PER_CATCH[1]`% of the total catch. Other abundant fish species included `r SPC_SUM$SPC_NMCO[2]` (`r SPC_SUM$PER_CATCH[2]`%), `r SPC_SUM$SPC_NMCO[3]` (`r SPC_SUM$PER_CATCH[3]`%), and `r SPC_SUM$SPC_NMCO[4]` (`r SPC_SUM$PER_CATCH[4]`%). There were _____ species at risk (SAR) captured in the `r FN011$YEAR` survey: ____________ (n=###). There were ______ SAR mortalities in `r FN011$YEAR`.

<!-- Add information about SAR species manually to ensure accuracy. -->

\newpage

**Table 1** Total number of individuals for all fish species caught in Inner Long Point Bay, Lake Erie during the Inner Bay Fish Community Hoop Net Survey in `r FN011$YEAR`. 

<!-- This section will add a table of species catch. -->

```{r SPC Table, echo = FALSE, results = 'asis', warning=FALSE}
#Set table border
heavy <- fp_border(color = "black", style = "solid", width = 2)
thin <-  fp_border(color = "black", style = "solid", width = 1)

#Create the table
SPC_TABLE <- SPC_SUM %>%
  arrange(SPC)%>%
  select(-c("SPC", "PER_CATCH"))%>%
  flextable() %>%
  align(j = 3, align = "right", part = "all")%>%
  width(j = 1, width = 1.7, unit = "in")%>%
  width(j = 2, width = 2.2, unit = "in")%>%
  font(fontname = "Raleway")%>%
  set_header_labels(SPC_NMCO = "Common Name", SPC_NMSC = "Scientific Name", CATCNT = "Count")%>%
  italic(j = 2, italic = TRUE, part = "body")%>%
  hline_top(border = heavy, part = "header")%>%
  hline(border = thin, part = "header")%>%
  hline_bottom(border = thin, part = "header")%>%
  hline_bottom(border = heavy, part = "body")
  
SPC_TABLE
```
